Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-09-05 manu-draft.qmd
minor fig aesthetic changes, added some latex equations for mixeff and gam

For @fig-saltempraw, salinity shows much higher inter-annual variability, but lower intra-year variation among stations. Trends are similar for bottom vs top, temperature shows stronger trend than salinity.

@@

@@

@@

Summary of a Generalized Additive Model evaluating frequency occurrence of seagrass versus year, number of days in a year when temperature exceeded the threshold, number of days in a year when salinity was below the threshold, and number of days in a year when both temperature and salinity were above or below thresholds.  All variables were fit as main effects, including interactions with year. edf: estimate degrees of freedom, ref.df: reference degrees of freedom, F: F-statistic. * p < 0.05, ** p < 0.005.

>>>>

For @fig-meteowqraw, salinity shows much higher inter-annual variability, but lower intra-year variation among stations. Trends are similar for bottom vs top, temperature shows stronger trend than salinity.

@@

$$
Y_{ij} = \beta_0 + \beta_1X_{ij} + u_i + \epsilon_{ij}
$$

@@

GAM notation:

$$
Y_i = \beta_0 + f_1\left(\text{Sal}_i\right) + f_2\left(\text{Temp}_i\right) + f_3\left(\text{Both}_i\right) + f_4\left(\text{Year}_i, \text{Sal}_i\right) + f_5\left(\text{Year}_i, \text{Temp}_i\right) + f_6\left(\text{Year}_i, \text{Both}_i\right)  + \epsilon_i
$$

@@

Summary of a Generalized Additive Model evaluating frequency occurrence of seagrass versus year, number of days in a year when temperature exceeded the threshold, number of days in a year when salinity was below the threshold, and number of days in a year when both temperature and salinity were above or below thresholds. All variables were fit as main effects, including interactions with year. edf: estimate degrees of freedom, ref.df: reference degrees of freedom, F: F-statistic. \* p \< 0.05, \*\* p \< 0.005.
